itle: "Worksheet: Introduction to Datasets"
subtitle: "STT 2860 Intro to Data Mgmt & Visualization" 
author: "PUT YOUR NAME HERE"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4 
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

***

This worksheet is mean to accompany [Dr. Thomley's Introduction to Datasets slides](https://stat-jet-asu.github.io/Slides/STT2860/IntroToDatasets.html#1).

***

### Packages Used

```{r}
library(HistData)
library(tidyverse)
library(nycflights13)
```


### Datasets in `R`

Use the `data()` function in the Console to see what datasets are available. [This reference](https://rstats101.com/built-in-datasets-in-r/) also explains how this function works. You can find it linked in our Essential Resources on AsULearn.


### The `Nightingale` Dataset

Investigate the `Nightingale` dataset from the HistData package.

#### Save the dataset to the Environment

```{r}
nightingale <- Nightingale
nightingale$date
head(nightingale, n = 4) 
# n is telling r to make 4 rows and the default is 6 and tail gives the bottom six rows.
```

#### Explore the structure of the dataset

```{r}
str(nightingale) # shows the values listed in the environment.
```


### The `insertname` dataset

Investigate another dataset from the HistData or other package.

#### Save the dataset to the Environment

```{r}
attributes(nightingale) 
names(nightingale) # shows variable names
dim(nightingale) # dimensions
```

#### Explore the structure of the dataset

```{r}

```


### Build a Dataset from Scratch

#### Create a dataset using `data.frame()` and explore

```{r}
dataset1 <- data.frame(
  ID = 1:5,
  gender = c("male", "male", "female", "female", "nonbinary"),
  height = c(71, 73, 64, 64, 66),
  weight = c(175, 225, 130, 125, 165)
)
```

#### Create a dataset using `tibble()` and explore

```{r}

```

#### Example containing missing data

```{r}

```


### Build a List from Scratch

#### Create a list of vectors using `list()` and explore 

```{r}

```

#### Create a list of datasets using `list()` and explore

```{r}

```


***
```{r}
sessionInfo()
```
The exclimation point ! means "not" in R
```{r}
sum(complete.cases(flights))
sum(!complete.cases(flights))
```

```{r}
GN <- data.frame(Times = c(9, 10, 11, 9, 9, 9, 9, 9, 9, 10, 10, 10), Names = c("Jeff", "George", "L", "Q", "W", "E", "R", "T", "Y", "U", "I", "O"))
GN
```

