---
title: "Worksheet: Introduction to Vectors"
subtitle: "STT 2860 Intro to Data Management & Visualization" 
author: "Ethan Farrell"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4 
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

------------------------------------------------------------------------

-   [Dr. Thomley's Introduction to Vectors slides](https://stat-jet-asu.github.io/Slides/STT2860/IntroVectors.html)
-   [Dr. Thomley's Patterned Vectors slides](https://stat-jet-asu.github.io/Slides/STT2860/PatternedVectors.html)

------------------------------------------------------------------------

### Packages Used

```{r packagesused}
# load all packages used here

```

### Using the `c()` Function

using the typeof() functiion you can see what type of vector you have.

#### logical vector

```{r}
logicalvector <- c(TRUE, TRUE, FALSE, TRUE)
```

#### numeric vector

```{r}
numericvector <- c(10, 2, 78, 5, 16)
```

#### character vector

```{r}
charectervector <- c("Alex", "Drew", "Jordan", "Riley")
```

#### mixed vectors

```{r}
v1 <- c(10, TRUE, 0.5)
v1
typeof(v1)
class(v1)
```
```{r}
v2 <- c("A", 10, TRUE, 0.5)
typeof(v2)
class(v2)
as.numeric(v2)
```
### as.numeric(v2) forces the class to be numeric but you will have missing values tha must be replaced

### Using the `:` Function

The : function creates a sequence of values that increments in steps of ±1 from the value on the left side of the : to the value on the right (or as close as it can get).
Generates sequences by steps of 1 for exam 1:5 1,2,3,4,5


#### increasing sequence

```{r}

```

#### decreasing sequence

```{r}

```

#### non-integer sequence

```{r}

```

### Using the `seq()` Function

*erase this and add your own notes*

#### function syntax

```         
seq(from = 1, to = 1, by = ((to - from)/(length.out - 1)), length.out = NULL, along.with = NULL, ...)
```

#### using parameter `by =`

```{r}
s1 <- seq(from = 10, to = 100,by = 10)
```

#### using parameter `length.out =`

```{r}
seq(from = 1, to = 51, length.out = 5)
```

#### using parameter `along.with =`

```{r}
seq(from = 100, to = 200, along.with = s1)
```

### Using the `rep`()\` Function

```{r}
text <- c("BOOM","SHAKA","LAKA")
rep(text, times = c(1,2,5))
rep(text, each = 5)
```


length out is making there a set number for the length, 5 variables 5 is the length

along.with makes the length the same as another

------------------------------------------------------------------------

```{r}
sessionInfo()
```
